The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
impl pract done

An alternative way of addressing this problem could be by including the application developers in the feedback loop.

----------------------------------------------------------------------

%       -How will our study help Axis? (More important)
The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed. [1980programs]

The main thing will be:
1. Our results found that feedback loop is, a) very important and b) the main thing that Axis wants to improve
2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
       [quotes re. budget/plan]:

   ``Managers involved in software evolution and software maintenance have great difficulty in
   defining, justifying, budgeting, staffing, supervising, accounting for, marshalling resources
   for, and assessing the work when coarse non-objective measures are used [4]. Things not
   appropriately named are often undervalued and treated as miscellaneous or trivial, since
   communication about them is made more cumbersome.'' %Chapin

       [quotes re. communication/stakeholders]:
       ``management must be thoroughly fami-liar with the organizational conventions and practices
       involved, in order to make intelligent decisions.'' //Swanson

       ``provide a realistic and practical classification to facilitate communication about, and the
       management of, software evolution and maintenance among researchers, practitioners, and their
       managers;'' //Chapin

%Whole bunch of Swanson stuff below.
% The implications for the management of software
% maintenance are several. First, insofar as maintenance
% is performed informally, i.e. in the absence of an
% established set of organizational conventions and prac-
% tices, the measurement of maintenance performance w i l l
% not be feasible. The establishment of a maintenance
% data base, a precondition to performance measurement,
% is not possible in the absense of organizational struc-
% ture. In informal situations, performance must be assessed informally.

% Secondly, in any given organization in which main-
% tenance performance is formally assessed, in terms of
% specific measures, management must be thoroughly fami-
% l i a r with the organizational conventions and practices
% involved, in order to make intelligent decisions. No
% single measure or set of measures w i l l i t s e l f reveal
% that maintenance is going "better" or "worse" than
% management has a right to expect or desire. Such a
% judgment must follow as a systemic inference from an
% analysis of the performance measurements, made in the
% context of f a m i l i a r i t y with the organizational struc-
% ture which made these measurements possible.

% Finally, in the absence of f a m i l i a r i t y with other,
% alternative organizational structures for performing
% maintenance, management w i l l be essentially unable to
% assess i t s own established structure. Nothing in the
% performance measurements made within the context of the
% established structure w i l l indicate the opportunity
% costs associated with this structure. Management must
% look outside, to the performance measurements and
% structures of other organizations, to assess what might
% reasonably be achieved through organizational change.

% In the context of a maintenance organizational
% structure and a particular set of data gathered in the
% performance of maintenance within this structure, i t
% is possible to derive some performance measures which
% should be appropriately "suggestive" to management.

% Measures of maintenance performance are
% not meaningful except within the context
% of the organizational structure(s) upon
% which they are based. p

3. Suggest to Axis that they improve their feedback loop by using the types

Also suggest that they keep evolving the API with reference to the laws

Implications for Practice tips: 
       3. Each implications for practice section should include descriptions of 
       a) problematic issue(s) being addressed, 
       b) the specific audience(s) to which implications are addressed, 
       c) a small number of recommendations about what the audience should/could/should not do based on the research findings, 
       d) an expected outcome of carrying out recommendation(s), and 
       e) some specific illustrations of what carrying out the recommendations might look like, perhaps in narrative form.

\url{https://www.princeton.edu/futureofchildren/publications/journals/article/index.xml?journalid=46&articleid=212&sectionid=1379}

>>>>

One way of finding the solution to this problem would be by including the application developers in the feedback loop. Since the application developers are on the receiving end of the changes, we believe that their needs have to be assessed before the problem can be solved. With our study we identified both that the law of Feedback System is of great importance to the case company and that it is one of the main aspects of the development of their API which they want to improve (!!!reword). One challenge of software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}. Based on this, we propose that our study which has granulated the activites is used as a basis for communicating the current stage of the evolution of their API. We hope that this classification can be used in its current form, to help quantify the activities and to provide an overview of them. We also hope that the approach we used can be used to predict which types of activites should be emphasised in the future evolution of the API. With our study we have also demonstrated that the classification of changes is achievable, which, in turn, should encourage the case company to follow suit (!!!casual).
